---
title: "Stat of BeeMedic usage"
output:
  html_document:
    df_print: paged
---



```{r message=FALSE, warning=FALSE}
#rm(list = ls(all = TRUE))

library(plotly)
library(tidyverse)
library(leaflet)
library(rgdal)
library(rgeolocate)
library(rgdal)
library(RColorBrewer)

```


Read data in 
```{r}
cygnetdb_temp <- read.csv("data/db12376021-cygnetuser_datatable2_shorttest.sql", header=FALSE, quote="'", na.strings="(") %>% as_tibble()
#cygnetdb_temp <- read_csv("data/db12376021-cygnetuser_datatable2_shorttest.sql", 
#                          trim_ws = TRUE, quoted_na= TRUE, col_names = FLASE) %>% as_tibble()

cygnetdb = cygnetdb_temp[!grepl("INSERT", cygnetdb_temp$V1),]
cygnetdb = cygnetdb[!grepl("null|rd_err", cygnetdb$V4),]
cygnetdb = cygnetdb[!grepl("`Serial_number`", cygnetdb$V3),]
cygnetdb = cygnetdb[!grepl("null", cygnetdb$V9),]
cygnetdb <- cygnetdb %>% dplyr::rename(IpAddress = V16) %>% mutate(IpAddress = as.character(IpAddress) %>% trimws(),  AccessDate = as.Date(sub(".", "", V1)))


```


Find vignette of rgeolocate at https://cran.r-project.org/web/packages/rgeolocate/vignettes/Introduction_to_rgeolocate.html 
MaxMind does openly release a more limited set of databases covering country and city data; these are also supported and can be obtained https://dev.maxmind.com/geoip/geoip2/geolite2/ . 



```{r}

file <- system.file("extdata","GeoLite2-Country.mmdb", package = "rgeolocate")
tmp <-  cygnetdb%>% select(IpAddress) %>% mutate(IpCountry = purrr::map(IpAddress, maxmind, file, c("country_code", "country_name")))
tmp <-            tmp   %>% unnest(IpCountry) %>% group_by(country_name) %>% 
  tally(name = "NumberOfUse") 
tmp %>% mutate(country_name = fct_reorder(country_name, NumberOfUse)) %>%  ggplot(aes(country_name, NumberOfUse)) + geom_col() + coord_flip()



```

### Customizied leaflet choropleth map


```{r}
mybins <- c(0,10,20,50,100, 200, 500,Inf)
library(rgdal)
world_spdf <- readOGR( 
  dsn= paste0(getwd(),"/DATA/world_shape_file/") , 
  layer="TM_WORLD_BORDERS_SIMPL-0.3",
  verbose=FALSE
)
 world_spdf@data <- left_join(world_spdf@data,tmp , by = c("NAME" = "country_name"))

mypalette <- colorBin( palette="YlOrBr", domain=world_spdf@data$NumberOfUse, na.color="transparent", bins=mybins)
 
# Prepare the text for tooltips:
mytext <- paste(
    "Country: ", world_spdf@data$NAME,"<br/>", 
    "Area: ", world_spdf@data$AREA, "<br/>", 
    "Number of useages: ", round(world_spdf@data$NumberOfUse, 2), 
    sep="") %>%
  lapply(htmltools::HTML)
 
# Final Map
leaflet(world_spdf) %>% 
  addTiles()  %>% 
  setView( lat=10, lng=0 , zoom=2) %>%
  addPolygons( 
    fillColor = ~mypalette(NumberOfUse), 
    stroke=TRUE, 
    fillOpacity = 0.9, 
    color="white", 
    weight=0.3,
    label = mytext,
    labelOptions = labelOptions( 
      style = list("font-weight" = "normal", padding = "3px 8px"), 
      textsize = "13px", 
      direction = "auto"
    )
  ) %>%
  addLegend( pal=mypalette, values=~NumberOfUse, opacity=0.9, title = "Number of useages (M)", position = "bottomleft" )


  
# save the widget in a html file if needed.
# library(htmlwidgets)
# saveWidget(m, file=paste0( getwd(), "/HtmlWidget/choroplethLeaflet5.html"))
```


Info on how to create leaflet maps are at https://rstudio.github.io/leaflet/ 

```{r}
library(maps)
mapStates = map("state", fill = TRUE, plot = FALSE)
leaflet(data = mapStates) %>% addTiles() %>%
  addPolygons(fillColor = topo.colors(10, alpha = NULL), stroke = FALSE)
```

## Popups

https://rstudio.github.io/leaflet/popups.html   
A common use for popups is to have them appear when markers or shapes are clicked. Marker and shape functions in the Leaflet package take a popup argument, where you can pass in HTML to easily attach a simple popup. 
```{r}
content <- paste(sep = "<br/>",
  "<b><a href='http://www.samurainoodle.com'>Samurai Noodle</a></b>",
  "606 5th Ave. S",
  "Seattle, WA 98138"
)

leaflet() %>% addTiles() %>%
  addPopups(-122.327298, 47.597131, content,
    options = popupOptions(closeButton = FALSE)
  )
```

## A choropleth map

A choropleth map (from Greek χῶρος "area/region" and πλῆθος "multitude") is a type of thematic map in which areas are shaded or patterned in proportion to a statistical variable that represents an aggregate summary of a geographic characteristic within each area, such as population density or per-capita income.

World boundaries geo.json downloaded from here.https://github.com/johan/world.geo.json

```{r}
WorldCountry <-geojsonio::geojson_read("data/countries.geo.json", what = "sp")
#Dataframe for choropleth map
Country <- c("Bulgaria","Pakistan","Turkey")
Projects <- c(2,1,6)
data <- data.frame(Country,Projects)
data_Map <- WorldCountry[WorldCountry$id %in% data$Country, ]
Map <- leaflet(data_Map) %>% addTiles() %>% addPolygons()
#basemap
#Map <- leaflet(WorldCountry) %>% addTiles() %>% addPolygons()

#set bin and color for choropleth map
bins <- c(0,1,2,3,4,5,6,7,8,9,10,Inf)
pal <- colorBin("YlOrRd", domain = data$Projects, bins = bins)

#set labels
labels <- sprintf(
  "<strong>%s</strong><br/>%g projects <sup></sup>",
  data$Country, data$Projects) %>% lapply(htmltools::HTML)

#add polygons,labels and mouse over effect
Map %>% addPolygons(
  fillColor = ~pal(data$Projects),
  weight = 2,
  opacity = 1,
  color = 'white',
  dashArray = '3',
  fillOpacity = 0.7,
  highlight = highlightOptions(
     weight = 5,
    color = "#666",
    dashArray = "",
    fillOpacity = 0.7,
    bringToFront = TRUE),
  label = labels,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto")
)
```
## Interactive choropleth map with R and leaflet 
This post explains how to build an interactive choropleth map with R and the leaflet package. A tooltip is available for each region on hover, and the map is 
https://www.r-graph-gallery.com/183-choropleth-map-with-leaflet.html

This tutorial uses a geospatial object stored in a shape file available here. Start by downloading the file:

```{r}
# Download the shapefile. (note that I store it in a folder called DATA. You have to change that if needed.)
download.file("http://thematicmapping.org/downloads/TM_WORLD_BORDERS_SIMPL-0.3.zip" , destfile="DATA/world_shape_file.zip")
# You now have it in your current working directory, have a look!
```
And load it in R

```{r}
# Read this shape file with the rgdal library. 
library(rgdal)
world_spdf <- readOGR( 
  dsn= paste0(getwd(),"/DATA/world_shape_file/") , 
  layer="TM_WORLD_BORDERS_SIMPL-0.3",
  verbose=FALSE
)

# Clean the data object
library(dplyr)
world_spdf@data$POP2005[ which(world_spdf@data$POP2005 == 0)] = NA
world_spdf@data$POP2005 <- as.numeric(as.character(world_spdf@data$POP2005)) / 1000000 %>% round(2)

# -- > Now you have a Spdf object (spatial polygon data frame). You can start doing maps!
```







```{r}
# Create a color palette for the map:
mypalette <- colorNumeric( palette="viridis", domain=world_spdf@data$POP2005, na.color="transparent")
mypalette(c(45,43))

# Basic choropleth with leaflet?
m <- leaflet(world_spdf) %>% 
  addTiles()  %>% 
  setView( lat=10, lng=0 , zoom=2) %>%
  addPolygons( fillColor = ~mypalette(POP2005), stroke=FALSE )

m
```


# Time series heatmap


```{r}
library(data.table)
library(ggplot2)
library(ggTimeSeries)
set.seed(1)
dtData = data.table(
      DateCol = seq(
         as.Date("1/01/2014", "%d/%m/%Y"),
         as.Date("31/12/2014", "%d/%m/%Y"),
         "days"
      ),
      ValueCol = runif(730)
   )
# you could also try categorical data with
# ValueCol = sample(c('a','b','c'), 730, replace = T)
p1 = ggplot_calendar_heatmap(
   dtData,
   'DateCol',
   'ValueCol'
)
ggplotly(p1)
# add new geoms

```

http://www.columbia.edu/~sg3637/blog/Time_Series_Heatmaps.html 



